\documentclass[twocolumn,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[sort]{natbib}
\usepackage{titling}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{amsmath,xspace}
\usepackage[backgroundcolor=yellow]{todonotes}
\usepackage[utf8]{inputenc}
\usepackage{bibentry}
\usepackage{float}
\usepackage[ttscale=.875]{libertine}
\usepackage{listings}
\usepackage{libertinust1math}
\usepackage{mdframed} %nice frames
\usepackage[format=plain,
            labelfont={bf,it},
            textfont=it]{caption}
\usepackage{listings}
\usepackage[hyphens]{url}
\usepackage[breaklinks]{hyperref}



\setlength{\columnsep}{5mm}


\author{Daniel Bittman \\ dbittman@ucsc.edu}
\title{NVKV: Building a KV Store for Non-Volatile Memory\\{\Large CMPS278:
Database Design and Implementation: Class Project\\\vspace{-2mm}Instructor: Shel Finkelstein}}

\newcommand{\etal}{\emph{et~al.}\xspace}
\newcommand{\bdb}{Berkeley DB\xspace}
\begin{document}
\biolinum
\maketitle
\libertine 
\renewcommand\ttdefault{lmtt}

\lstset{ 
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\ttfamily\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
}





\section*{Abstract}


Byte-addressable non-volatile memory (BNVM) will change the memory hierarchy, and
applications must be ready to exploit the advantages afforded by these
technologies while minimizing their weaknesses. Changes in power use
characteristics, consistency requirements, and wear-out means that systems
designed for other memory hierarchies and technologies are not the best fit for
BNVM. We need to think about how to best build systems and applications with the
need for fine-grained consistency, the need to minimize writes to reduce power
and wear-out, and the desire to provide low-latency access to persistent storage
without the operating system getting in the way at every turn.


One example of applications which could be redesigned is key-value stores. We
have built NVKV, a key-value store that attempts to minimize writes while
providing low-latency access, all while remaining consistent regardless of power
cycles and providing backwards compatibility with \bdb. It does this through the
use of transactional memory, or at least what we expect transactional memory to
look like, while minimizing transaction sizes. It provides insert and lookup
functionality with a significant performance improvement over \bdb, while
providing an improvement in consistency safety with respect to power cycles, and
provides better quality of service insert operations. Finally, we demonstrate
that a new Cuckoo hashing variant can reduce data movement and improve the
performance of rehashing significantly.


\input{intro}

\input{background}

\input{design}

\input{impl}

\input{results}

\input{related}

\input{concl}

\section*{Availability}
The code and data for this project can be found
at \url{https://github.com/dbittman/cmps278}.

\section*{Acknowledgements}

Thanks to Matt Bryson for helping collect some of the papers for energy use
in PCM and DRAM (these results were used for another project in the SSRC in a
more detailed manner, but are mentioned here because they are relevant to
the motivation).

\bibliographystyle{plain}
\bibliography{bib/csrg,main,pcm_hardware}

\end{document}

